\papertitle

### 2012-10-13 manuscript.tex
new heat map and text

%----------------------------------------------------------------------------%
% PACKAGES
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\providecommand{\norm}[1]{\lVert#1\rVert}

@@

%............................................................................%
\subsubsection{Motion Model}
Our motion model (Eq.~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Eq.~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the state of the $i^\text{th}$ particle at time $t$, $\Sigma$ 
is a chosen covariance matrix, and $b$ is vector of the height and width of 
the camera frame.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
The experiments presented in this work use a diagonal covariance matrix 
with variance 256, and an $\epsilon$ of 0.3. We find that the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample all of the pixel space. This prevents overconfidence and collapse, 
and decreases reacquisition delay.

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) implements a sampling
approach to motion tracking via na\"{i}ve background subtraction[CITATION].
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
The system provides the emission model with $f_0$, the frame representing 
the background and $f_t$, the most recent frame captured. The model assigns 
a weight $w^{[i]}_t$ to each particle $x^{[i]}_t$, proportional to the color 
distance in RGB space between the pixels of $f_0$ and $f_t$ at the location 
$x^{[i]}_t$. Hence, particles are more likely to be resampled in portions of 
the image which appear different from the background.

For the experiments presented in this work, we assumed that neither the bird 
nor any other moving object were visible in the first frame captured on system 
start. We saved the first frame captured by the system, and provided it as 
the background frame $f_0$ for every iteration of the particle filter. This 
resulted in a sampling approach to na\"{i}ve background subtraction.

Na\"{i}ve background subtraction is brittle to changes in the scene over 
time[CITATION]. However, we found it very efficient, and reliable enough for the 
short time spans necessary for H$^2$Bird to successfully negotiate narrow 
openings, which are typically less than five seconds. Substituting $f_0$ 
with a more sophisticated extraction of the background would implement a 
more sophisticated approach to background subtraction, with no changes to 
the underlying motion tracking filter.

@@

@@

@@

>>>>

%----------------------------------------------------------------------------%
% PACKAGES
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{amsmath}

\newlength\eqnindent
\newlength\eqncolwid
\newcommand\eqntext[2][0pt]{%
  \setlength\parindent{0pt}%
      \setlength\eqnindent{#1}\setlength\eqncolwid{\linewidth}%
  \setlength\eqncolwid{\dimexpr\linewidth-\eqnindent}%
  \hspace*{\eqnindent}\parbox{\eqncolwid}{#2}%
}

@@

%............................................................................%
\subsubsection{Motion Model}
Our motion model (Eq.~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Eq.~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the state of the $i^\text{th}$ particle at time $t$, $\Sigma$ 
is a chosen covariance matrix, and $b$ is vector of the height and width of 
the camera frame.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
The experiments presented in this paper used a diagonal covariance matrix 
with variance 256, and an $\epsilon$ of 0.3. We find that the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample all of the pixel space. This prevents overconfidence and collapse, 
and decreases reacquisition delay.

%............................................................................%
\subsubsection{Emission Model}
Our emission model (Eq.~\ref{eq:emission_model}) effectively performs.

@@

The model of the ground station combines both the camera model and the
computational model for pose estimation. The camera model contains both a
latency, which would occur in between the "camera" and "ornithopter dynamics"
in Fig.~\ref{fig:block_diagram}, and a model for the viewing angle. The
viewing angle for the camera is modeled as a pixel map from one edge of a
63$^{\circ}$ viewing triangle to the other. The camera has an image width of
640 pixels. The desired heading angle in degrees for a given distance from the
camera is calculated according to Equation~\ref{eq:desired_heading}, where d
is the distance of the robot in front of the camera and x is the horizontal
position of the robot relative to the center of the window in meters. This
formula models the fact that the camera cannot determine the depth of the
robot.

\begin{equation} \label{eq:desired_heading} \text{Desired heading} =
\frac{640\text{px}}{2*\text{d}*\tan{\frac{63^{\circ}}{2}}}*\frac{63^{\circ}}{640\text{px}}*\text{x}
\end{equation}

The computational model consists of the latency for the operations required to
run the particle filter and calculate the input to send to the robot.

@@

To measure the capture latency of the camera, we alternatively flashed black
and white color in front of the camera and measured the time lapse before it
detected the color change. We averaged this result over 50 trials to determine
the capture latency.

To compute the particle filter latency, we used system timers to determine the
average time from the start of computation to the end of computation.

@@

The latency that we measured for the camera was 25ms and the measured
partiicle filter computational latency was 12.5ms.
